Komols Complexity, Coresets, and Sketches in Machine Learning

### 2018-12-18 komlos.tex
before changes
colt style

\documentclass{article} % For LaTeX2e
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage[noend]{algorithmic}
\usepackage{algorithm}
\usepackage[margin=1in]{geometry}
\usepackage{xcolor}
\usepackage{amsfonts}
\usepackage{ amssymb }

\newtheorem{theorem}{Theorem}[section]
\newtheorem{conjecture}{Conjecture}[section]
%\newtheorem{claim}[theorem]{Claim}
\newtheorem{lemma}[theorem]{Lemma}
%\newtheorem{remark}[theorem]{Remark}
%\newtheorem{definition}[theorem]{Definition}
%\newtheorem{observation}[theorem]{Observation}
%\newtheorem{corollary}[theorem]{Corollary}
%\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{fact}[theorem]{Fact}

@@

%\newtheorem*{definition*}{Definition}
\newtheorem{definition}{Definition}
\newtheorem{claim}{Claim}
%\newtheorem{theorem}{Theorem}

\title{Sketching for Density Estimation}
\date{\nonumber}

\author{
Zohar Karnin\\Amazon\\zkarnin@amazon.com
\and
Edo Liberty\\Amazon\\libertye@amazon.com
}

@@

\el{I believe we that the correctness of the Komlos conjecture implies equivalence between coresets limited to the input and general coresets. Specifically, a constructive positive resolution will give an algorithm for converting any coresets to signs $\sigma$ and select inputs from a sequence.}

@@

In \cite{DBLP:journals/corr/abs-1802-01751} (see paragraph before Lemma 2.2) they manage to obtain a coreset (with equal weights) of size $\sqrt{d \log(1/\eps)}/\eps$ for any kernel with certain properties. The do so by considering a matrix whose rows correspond to all the vectors in an $\eps$-net over the space, and columns correspond to the $n$ data points. Calling that matrix $A$, $A_{q,x} = K(q,x)$. They bound the discrepancy of the matrix defined as $\min_s \|As\|_\infty$ where $s$ is a sign vector by using a bound 
$$ \min_s \|As\|_\infty \leq \sqrt{\log(N)} \|A\|_{\gamma_2} $$
Here, $N$ is the size of the $\eps$ net and the $\gamma_2$ norm is 
$$ \|A\|_{\gamma_2} = \min_{B,C: A=BC^T} \text{max norm of a row of B or C}$$
They prove that for psd kernel $K$, $\|A\|_{\gamma_2} \leq 1$ (in fact it is equal to 1). Now, back to our case. For any fixed power $k$ we know that $K(x,q)=\ip{x,q}^k$ is a psd kernel, hence its corresponding matrix $A_k$ has $\gamma_2$ norm bounded by $1$. Now, the logistic function can be written in a taylor expansion whose coefficients, in absolute value, sum to a constant $C$. It follows that the $A$ matrix for the logistic function has a $\gamma_2$ norm bounded by $C$. The same arguments as in  \cite{DBLP:journals/corr/abs-1802-01751} can now prove that its discrepancy is bounded by $\sqrt{\log(N)} \approx \sqrt{d\log(1/\eps)}$

>>>>

\documentclass[anon,12pt]{colt2019} % Anonymized submission
% \documentclass[12pt]{colt2019} % Include author names

% The following packages will be automatically loaded:
% amsmath, amssymb, natbib, graphicx, url, algorithm2e

\title[Komols Complexity, Coresets, and Sketches in Machine Learning]{Komols Complexity, Coresets, and Sketches in Machine Learning}
\usepackage{times}
% Use \Name{Author Name} to specify the name.
% If the surname contains spaces, enclose the surname
% in braces, e.g. \Name{John {Smith Jones}} similarly
% if the name has a "von" part, e.g \Name{Jane {de Winter}}.
% If the first letter in the forenames is a diacritic
% enclose the diacritic in braces, e.g. \Name{{\'E}louise Smith}

% Two authors with the same address
% \coltauthor{\Name{Author Name1} \Email{abc@sample.com}\and
%  \Name{Author Name2} \Email{xyz@sample.com}\\
%  \addr Address}

% Three or more authors with the same address:
% \coltauthor{\Name{Author Name1} \Email{an1@sample.com}\\
%  \Name{Author Name2} \Email{an2@sample.com}\\
%  \Name{Author Name3} \Email{an3@sample.com}\\
%  \addr Address}

\usepackage{amsmath}
%\usepackage{amsthm}
\usepackage[noend]{algorithmic}
\usepackage{algorithm}
%\usepackage[margin=1in]{geometry}
\usepackage{xcolor}
\usepackage{amsfonts}
\usepackage{ amssymb }

%\newtheorem{theorem}{Theorem}[section]
%\newtheorem{conjecture}{Conjecture}[section]
%\newtheorem{claim}[theorem]{Claim}
%\newtheorem{lemma}[theorem]{Lemma}
%\newtheorem{remark}[theorem]{Remark}
%\newtheorem{definition}[theorem]{Definition}
%\newtheorem{observation}[theorem]{Observation}
%\newtheorem{corollary}[theorem]{Corollary}
%\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{fact}[theorem]{Fact}
%\newtheorem*{definition*}{Definition}
%\newtheorem{definition}{Definition}
%\newtheorem{claim}{Claim}
%\newtheorem{theorem}{Theorem}

@@

% Authors with different addresses:
\coltauthor{%
 \Name{Zohar Karnin} \Email{zkarnin@amazon.com}%\\ \addr Address 1
 \AND
 \Name{Edo Liberty} \Email{libertye@amazon.com}%\\ \addr Address 2%
}

@@

\el{I believe that the correctness of the Komlos conjecture implies equivalence between coresets limited to the input and general coresets. Specifically, a constructive positive resolution will give an algorithm for converting any coresets to signs $\sigma$ and select inputs from a sequence.}

@@

In \cite{DBLP:journals/corr/abs-1802-01751} (see paragraph before Lemma 2.2) they manage to obtain a coreset (with equal weights) of size $\sqrt{d \log(1/\eps)}/\eps$ for any kernel with certain properties. They do so by considering a matrix whose rows correspond to all the vectors in an $\eps$-net over the space, and columns correspond to the $n$ data points. Calling that matrix $A$, $A_{q,x} = K(q,x)$. They bound the discrepancy of the matrix defined as $\min_s \|As\|_\infty$ where $s$ is a sign vector by using a bound 
$$ \min_s \|As\|_\infty \leq \sqrt{\log(N)} \|A\|_{\gamma_2} $$
Here, $N$ is the size of the $\eps$ net and the $\gamma_2$ norm is 
$$ \|A\|_{\gamma_2} = \min_{B,C: A=BC^T} \text{max norm of a row of B or C}$$
They prove that for psd kernel $K$, $\|A\|_{\gamma_2} \leq 1$ (in fact it is equal to 1). Now, back to our case. For any fixed power $k$ we know that $K(x,q)=\ip{x,q}^k$ is a psd kernel, hence its corresponding matrix $A_k$ has $\gamma_2$ norm bounded by $1$. Now, the logistic function can be written in a taylor expansion whose coefficients, in absolute value, sum to a constant $C$. It follows that the $A$ matrix for the logistic function has a $\gamma_2$ norm bounded by $C$. The same arguments as in  \cite{DBLP:journals/corr/abs-1802-01751} can now prove that its discrepancy is bounded by $\sqrt{\log(N)} \approx \sqrt{d\log(1/\eps)}$
